---
title: "EucFACE parameter list 2020"
author: "Mingkai Jiang"
date: "3/23/2020"
output: pdf_document
---

Any questions, contact Mingkai Jiang (m.jiang@westernsydney.edu.au)


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

    ### source the functions to start the calculations.
    source("prepare.R")

    ###
    
    ### assign aco2 and eco2 rings
    aCO2_rings <- c(2,3,6)
    eCO2_rings <- c(1,4,5)
    
```

## General site description
Site elevation: 22 m above sea level

Site N deposition: 

Six plots at EucFACE, centered at: 

**Table 1.** Plot latitude and longitude information at EucFACE

``` {r, echo=FALSE, fig.width = 7, fig.align="center", warning=F}
    siteDF <- read.csv("temp_files/site_information.csv")

    kable(siteDF)    

```

These plots are hexadecagons that are 25 m in diameter, with 32 vertical stand pipes for CO~2~ release. Plot area = ~490 m^2^. More detailed site description can be obtained from Jiang _et al._ (2020). 


The dominant species is _Eucalyptus tereticornis_ Sm., accounting for >98% of the stem area. Stem diameter is measured at breast height of 1.3m (DBH). Only trees with diameter > 10 cm at the start of the experiment (i.e. 2012) were included. Also, all dead trees (by 2019) were excluded. The estimated stem biomass was based on an allometric relationship in Paul _et al._ (2013), which uses DBH and height to estimate biomass. Here, the estimated stem biomass refers to dry matter. To obtain stem biomass in unit of carbon, you need to multiple dry matter by an average carbon fraction of 0.46. 


**Table 2**. Biometrical description for plots/trees:
``` {r, echo=FALSE, fig.width = 7, fig.align="center", warning=F, message=F}
    wood_table <- make_wood_table(ring_area=FACE_ring_area)

    #wood_table1 <- wood_table[,c("Trt", "Diameter.mean", "BA.mean", "Biomass.mean",
    #                             "Height.mean", "Trees.mean")]
    #
    #wood_table2 <- wood_table[,c("Trt", "Diameter.sd", "BA.sd", "Biomass.sd",
    #                             "Height.sd", "Trees.sd")]

    kable(wood_table, digits=2, col.names = c("Ring", "Mean diameter", 
                                               "Stem biomass", "Basal area", "Max height", 
                                               "Tree density","Trt"))  
    
    #kable(wood_table2, digits=2, col.names = c("Trt", "Mean diameter sd", "Basal area sd",
    #                                           "Stem biomass sd", "Max height sd", 
    #                                           "Tree density sd")) 

```

Units are: Mean diameter = cm / tree, Basal area = cm^2^ / ha,
Stem biomass = mg / ha, Max height = m, Tree density = no. tree / ha


The understorey is a diverse mixture of C3 and C4 vegetation, with _Microlaena stipoides_ – a C3 perennial grass dominating (~ accounting for 70% of the herbaceous biomass). Note that understorey biomass respond very rapidly to changes in rainfall (Pathare et al., 2018).


## Soil extractable water and texture 

_Note:_ same as what's assumed in Medlyn _et al._ (2016)

Total plant extractable soil water = 300 mm
Rooting depth = 2 m 
Effective field capacity = 530 mm (= 0.265 m3 m-3)
Effective wilting point = 230 mm (= 0.115 m3 m-3)
Notes: “effective” because it averages over the different soil layers (taking into account differences in texture, bulk density, wilting points estimated from release curves). 
Field capacity was estimated from actual total storage estimates based on neutron probe measurements. This is fairly high because the soil drains poorly/slowly, so more water is actually available to the plant.

Surface soil texture (upper 45 cm) for Clarenden sand: 80 ± 8% sand, 9 ± 5% silt, 11 ± 3% clay
Source: Teresa Gimeno, Burhan Amiji & D. Ellsworth


## Soil chemical and physical properties

**Table 3**. Soil physical properties
``` {r, echo=FALSE, fig.width = 7, fig.align="center", warning=F}
    soil_bulk_density <- make_soil_bulk_density()
    soil_bulk_density$Trt <- "aCO2"
    soil_bulk_density$Trt[soil_bulk_density$ring%in%c(1,4,5)] <- "eCO2"
    soilBK <- summaryBy(bulk_density_kg_m3~Trt+Depth, FUN=c(mean, sd),
                        data=soil_bulk_density, na.rm=T, keep.names=T)

    kable(soilBK)    

```

**Table 4**. Soil nutrient concentrations
``` {r, echo=FALSE, fig.width = 7, fig.align="center", warning=F}
    soil_chemical_table <- make_soil_chemical_property_table(bk_density=soil_bulk_density)
    
    kable(soil_chemical_table,col.names = c("Depth", "pH", 
                                            "totC", "totN", "totPppm", 
                                             "pH_sd", 
                                            "totC_sd", "totN_sd", "totPppm_sd"))    

```





## 






## References cited:

Jiang _et al._ (2013). The fate of carbon in a mature forest under carbon dioxide enrichment. _Nature._.

Medlyn _et al._ (2016). EucFACE modeling. _Glob. Chang. Biol._.

Pathare _et al._ (2018). EucFACE understorey. _Glob. Chang. Biol._.

Paul _et al._ (2013). Development and testing of allometric equations for estimating aboveground biomass of mixed-species environmental plantings. _For. Ecol. Manage._ **310**, 483-494.


